Preprocess turk annotations =

### 2019-12-14 annotations/face_hands/analysis/preprocess_turk_segmentations.Rmd
Updates to .Rmd to preprocess segmentation hits

```{r}

```
# Preprocessing

@@

```{r}
total_area = jd$Answer.annotatedResult.inputImageProperties.height[1] * jd$Answer.annotatedResult.inputImageProperties.width[1]
d.raw <- d.raw %>%
  mutate(detection_area = (height*width)/total_area)

## plot detection area by detection type
ggplot(d.raw, aes(x=label, y=log(detection_area))) +
  geom_boxplot()

## faces tend to appear towards the top of the image (i.e. 0 pixel coordinates, or upper visual field)
ggplot(d.raw, aes(x=label, y=top)) +
  geom_boxplot()

@@

### Write out csv for use in analysis
```{r}
write_csv(d.raw,'turk_segmentations_dec12.csv')
```

>>>>

``
# Preprocessing

@@

```{r}
total_area = jd$Answer.annotatedResult.inputImageProperties.height[1] * jd$Answer.annotatedResult.inputImageProperties.width[1]
d <- d.raw %>%
  mutate(detection_area = (height*width)/total_area)

## plot detection area by detection type
ggplot(d, aes(x=label, y=log(detection_area))) +
  geom_boxplot()

## faces tend to appear towards the top of the image (i.e. 0 pixel coordinates, or upper visual field)
ggplot(d, aes(x=label, y=top)) +
  geom_boxplot()

@@

### Write out csv for use in analysis
```{r}
write_csv(d,'turk_segmentations_dec12.csv')
```

```{r}
d <- d %>%
  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7])
```

```{r eval=FALSE}

unique_images = d$full_image_path
for (image in unique_images){
  this_image_rgb <- image_read(image)
  img <- image_draw(this_image_rgb)
  a <- d %>%
    filter(full_image_path %in% image)

  rect(a$left, a$top+a$height, a$left+a$width, a$top)
  text(a$left+10, a$top+10, a$label)

  annotated_file = paste0(unique(a$short_image_path), 'turk-annotated.jpg')
  image_write(img, annotated_file)
  dev.off()
}

```{r}
faces <- d %>%
  filter(label =="Face")

rect(faces$left, faces$top+faces$height, faces$left+faces$width, faces$top)
text(faces$left+10, faces$top+10, faces$label)
```

```{r}  
child_hand <- d %>%
  filter(label =="Child hand")

rect(child_hand$left, child_hand$top+child_hand$height, child_hand$left+child_hand$width, child_hand$top)
text(child_hand$left+10, child_hand$top+10, child_hand$label)
